---
title: "thesis-sentiment"
author: "Nick"
date: "4/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tidyverse)
library(pdftools)
library(tidytext)
library(ggplot2)
library(rvest)
library(httr)
library(pipeR) #(see https://renkun-ken.github.io/pipeR-tutorial/Pipe-operator/Pipe-for-side-effect.html)
#library("svMisc") (for progress bar during reading files maybe..)
```

Query urls already prepared from the browser, ready to be read into R with rvest

```{r urls, echo=TRUE}
indbio_url <- "https://odr.chalmers.se/simple-search?location=%2F&query=&rpp=50&sort_by=dc.date.issued_dt&order=desc&filter_field_1=has_content_in_original_bundle&filter_type_1=equals&filter_value_1=true&filter_field_2=title&filter_type_2=notcontains&filter_value_2=och&filter_field_3=title&filter_type_3=notcontains&filter_value_3=hos&filter_field_4=title&filter_type_4=notcontains&filter_value_4=f%C3%B6r&filter_field_5=title&filter_type_5=notcontains&filter_value_5=av&filter_field_6=subject&filter_type_6=equals&filter_value_6=Industrial+Biotechnology"
sysbio_url <- "https://odr.chalmers.se/simple-search?location=%2F&query=&rpp=50&sort_by=dc.date.issued_dt&order=desc&filter_field_1=has_content_in_original_bundle&filter_type_1=equals&filter_value_1=true&filter_field_2=title&filter_type_2=notcontains&filter_value_2=och&filter_field_3=title&filter_type_3=notcontains&filter_value_3=hos&filter_field_4=title&filter_type_4=notcontains&filter_value_4=f%C3%B6r&filter_field_5=title&filter_type_5=notcontains&filter_value_5=av&filter_field_6=subject&filter_type_6=equals&filter_value_6=Bioinformatics+and+Systems+Biology"
food_url <- "https://odr.chalmers.se/simple-search?location=%2F&query=&rpp=60&sort_by=dc.date.issued_dt&order=desc&filter_field_1=has_content_in_original_bundle&filter_type_1=equals&filter_value_1=true&filter_field_2=title&filter_type_2=notcontains&filter_value_2=och&filter_field_3=title&filter_type_3=notcontains&filter_value_3=hos&filter_field_4=title&filter_type_4=notcontains&filter_value_4=f%C3%B6r&filter_field_5=title&filter_type_5=notcontains&filter_value_5=av&filter_field_6=subject&filter_type_6=equals&filter_value_6=Food+Science"
kth_to_17_url <-   "http://kth.diva-portal.org/smash/resultList.jsf?query=&language=en&searchType=UNDERGRADUATE&noOfRows=50&sortOrder=relevance_sort_desc&sortOrder2=title_sort_asc&onlyFullText=false&sf=all&aq=%5B%5B%5D%5D&aqe=%5B%5D&aq2=%5B%5B%7B%22dateIssued%22%3A%7B%22from%22%3A%222015%22%2C%22to%22%3A%222020%22%7D%7D%2C%7B%22organisationId%22%3A%225903%22%2C%22organisationId-Xtra%22%3Atrue%7D%5D%5D&af=%5B%22hasFulltext%3Atrue%22%2C%22language%3Aeng%22%5D"
kth_from_18_url <- "http://kth.diva-portal.org/smash/resultList.jsf?query=&language=en&searchType=UNDERGRADUATE&noOfRows=50&sortOrder=relevance_sort_desc&sortOrder2=title_sort_asc&onlyFullText=false&sf=all&aq=%5B%5B%5D%5D&aqe=%5B%5D&aq2=%5B%5B%7B%22organisationId%22%3A%22879224%22%2C%22organisationId-Xtra%22%3Atrue%7D%5D%5D&af=%5B%22personOrgId%3A879224%22%2C%22hasFulltext%3Atrue%22%2C%22language%3Aeng%22%2C%22categoryId%3A11500%22%2C%22categoryId%3A11528%22%5D"
su_url <- "https://su.diva-portal.org/smash/resultList.jsf?dswid=61&af=%5B%22language%3Aeng%22%2C%22hasFulltext%3Atrue%22%2C%22thesisLevel%3AH2%22%5D&p=1&fs=true&language=en&searchType=UNDERGRADUATE&query=&aq=%5B%5B%5D%5D&aq2=%5B%5B%7B%22dateIssued%22%3A%7B%22from%22%3A%222015%22%2C%22to%22%3A%222020%22%7D%7D%2C%7B%22organisationId%22%3A%22535%22%2C%22organisationId-Xtra%22%3Atrue%7D%5D%5D&aqe=%5B%5D&noOfRows=50&sortOrder=relevance_sort_desc&sortOrder2=title_sort_asc&onlyFullText=false&sf=all"

```

Now the functions to read the metadata from ODR/Diva and download the pdf files programmatically.

```{r functions}
get_chalmersodr_thesis <- function(url){
  #stopifnot(is.character(url) == TRUE)
  url %>% 
    read_html() %>%
    {
      tibble(year = html_nodes(., xpath = '//td[@headers="t1"]') %>% html_text(),
            title = html_nodes(., xpath = '//td[@headers="t2"]') %>% html_text(),
            author = html_nodes(., xpath = '//td[@headers="t3"]') %>% html_text(),
            # xpath expression checkes for the string "handle" in all href attributes              and returns them 
            id = html_nodes(., xpath = '//a[contains(@href,"handle")]/@href') %>%
                  html_text() %>% 
                  str_sub(-6),
            group = str_sub(url, -22)
            )
    } %>% 
    mutate(link = map_chr(url, function(url) {str_c("https://odr.chalmers.se/bitstream/20.500.12380/",
                                   url, "/1/", url, ".pdf", collapse = "")}
                          ),
           group = case_when(
             str_detect(group, "Food") ~ "Food",
             str_detect(group, "strial") ~ "IndBio",
             str_detect(group, "Systems") ~ "SysBio")
           )
}

get_diva_thesis <- function(url){
  stopifnot(is.character(url) == TRUE)
  url %>% 
    read_html() %>%
    {
      tibble(
        title = html_nodes(., xpath = '//a[@class="titleLink singleRow linkcolor"]') %>% html_text(),
        year = html_nodes(., xpath = '//a[@class="titleLink singleRow linkcolor"]//following-sibling::span[position() < 2]') %>% html_text(),
        author= html_nodes(., xpath = '//div[@class="ui-button ui-widget ui-state-default ui-corner-all ui-button-text-icon-left toggleOrganisation"]') %>% html_text(),
        link = html_nodes(., xpath = '//a[contains(@href,"get/diva2")]/@href') %>% html_text()
      )
    } %>% 
    mutate(link = map_chr(link, function(link) {
                                  ifelse(test = str_detect(url, "kth"),
                                         yes = str_c("http://kth.diva-portal.org/smash/", link, collapse = ""),
                                         no = str_c("http://su.diva-portal.org/smash/", link, collapse = ""))
                                  }
                  ),
           id = str_extract(link, "\\d{6,7}"),
           group = ifelse(str_detect(url, "kth"), "KTH", "SU")
    )
}

download_pdf <- function(link, id, group){
  dest_folder <- str_c("./", group, "/", collapse = "")
  if(!dir.exists(dest_folder))
    dir.create(dest_folder)
  
  dest_file <- str_c(dest_folder, id, ".pdf", collapse = "")
  if(!file.exists(dest_file)) {
    sleep <- sample(2:8, 1)
    print(paste("Pausing for ", sleep, "seconds"))
    Sys.sleep(sleep)
    download.file(link, destfile = dest_file)
  }
  else{
    print("File already exists. . . ")
    #Sys.sleep(2)
  }
}
```

Let's start by gathering some (meta)data on the thesis from their online repositories. Chalmers first

```{r}
chalmers_thesis <- map_dfr(c(indbio_url, sysbio_url, food_url) ,
                     .f = get_chalmersodr_thesis) 
```
then KTH,
```{r}
kth_thesis <- map_dfr(c(kth_to_17_url, kth_from_18_url), .f = get_diva_thesis)
```
and last, SU
```{r}
su_thesis <- get_diva_thesis(su_url)
```
Since they all have the same columns we can can stack them all toghether in one tibble
```{r}
all_thesis <- bind_rows(chalmers_thesis, kth_thesis, su_thesis)
```

We can taka a look at what we have with some graphs:
```{r}
all_thesis %>% 
  count(group, sort = TRUE) %>% 
  mutate(group = reorder(group, n)) %>% 
  ggplot(aes(group, n)) +
  geom_col() +
  coord_flip()

all_thesis %>% 
  group_by(group) %>% #filter(group == "KTH") %>% 
  count(year)
```



```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
